Exploratory Plots

### 2023-11-20 Code/R/RMarkdown/EntropyPlots.Rmd
best estimators

---
title: "Exploratory Plots"
author: "Alejandro C. Frery"
date: "2023-10-16"
output: html_document
#html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(plotly)
library(knitr)
library(rgl)
```

@@

  entropy <- term1 + term2 
  return(entropy)
}
```

```{r PlotGammaSAR, echo=FALSE}
mu <- seq(.1, 10, length.out=500)

EntropyL1 <- entropy_gamma_sar(L=1, mu)
EntropyL3 <- entropy_gamma_sar(L=3, mu)
EntropyL8 <- entropy_gamma_sar(L=8, mu)
EntropyL12 <- entropy_gamma_sar(L=12, mu)
EntropyL100 <- entropy_gamma_sar(L=100, mu)

muEntropy <- data.frame(
  mu, EntropyL1, EntropyL3, EntropyL8, EntropyL12, EntropyL100
)

muEntropy.molten <- melt(muEntropy, measure.vars = 2:6, value.name = "Entropy", variable.name = "Looks")

ggplot(muEntropy.molten, aes(x=mu, y=Entropy, col=Looks)) +
  geom_line() +
  theme_pander()

@@

```{r PlotGI0, echo=FALSE}
mu <- seq(1, 10, length.out = 500)
alpha <- seq(-20, -2, length.out = 500)

entropy <- outer(mu, alpha, FUN = function(mu, alpha) entropy_gI0(mu, alpha, L = 1))

#
persp(x = mu, y = alpha, z = entropy, col = "lightblue", border = "blue")

open3d()

persp3d(x = mu, y = alpha,z = entropy, col = "lightblue", border = "blue")

#-----
mu <- seq(1, 10, length.out=200)
alpha <- seq(-2, -20, length.out=200)

entropyL1 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=1))
entropyL3 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=3))
entropyL8 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=8))
entropyL12 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=12))
entropyL100 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=100))

fig <- plot_ly( x = alpha, y = mu,    showscale = FALSE)

fig <- fig %>% add_surface(z = ~entropyL1, colorscale = list(c(0,1),c("rgb(255,107,184)","rgb(128,0,64)")),  name = "L=1")
fig <- fig %>% add_surface(z = ~entropyL3, colorscale = list(c(0,1),c("rgb(107,184,255)","rgb(90,90,124)")),  name = "L=3")
fig <- fig %>% add_surface(z = ~entropyL8,  colorscale = list(c(0,1),c("rgb(247,226,157)","rgb(255,192,7)")),  name = "L=8")
fig <- fig %>% add_surface(z = ~entropyL12, colorscale = list(c(0,1),c("rgb(107,255,184)","rgb(0,124,90)")),  name = "L=12")
fig <- fig %>% add_surface(z = ~entropyL100, colorscale = list(c(0,1),c("rgb(182,142,242)","rgb(104,3,255)")),  name = "L=100")

fig <- fig %>% layout(
  scene = list(
    xaxis = list(title = "alpha"),
    yaxis = list(title = "mu"),
    zaxis = list(title = "Entropy")
  )
)

fig

>>>>

---
title: "Exploratory Plots"
author: "Alejandro C. Frery"
date: "2023-10-16"
output: pdf_document

# output: 
#   pdf_document:
#     toc: true
#     toc_depth: 2
#html_document
header-includes:
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)

library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(invgamma)
library(tidyverse)
library(scales)
library(RColorBrewer)
library(ggsci)
library(wesanderson)
library(ggpubr)
library(patchwork)
options(kableExtra.latex.load_packages = FALSE)
library(devtools)
devtools::install_github("haozhu233/kableExtra")
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
theme_set(theme_bw()  +
            theme(text=element_text(family="serif"),
                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
)
# Helpful for latex tables
# library(xtable)
# options(xtable.caption.placement='top',
#         xtable.table.placement='!t',
#         xtable.include.rownames=F,
#         xtable.comment=F)
# #library(rgl)

source("../MainFunctions/gamma_sar_sample.r")
source("../MainFunctions/entropy_gamma_sar.r")

source("../MainFunctions/van_es_estimator.r")
source("../MainFunctions/correa_estimator.r")
source("../MainFunctions/ebrahimi_estimator.r")
source("../MainFunctions/noughabi_arghami_estimator.r")
source("../MainFunctions/vasicek_estimator.r")
source("../MainFunctions/al_omari_1_estimator.r")
source("../MainFunctions/al_omari_2_estimator.r")

source("../MainFunctions/bootstrap_van_es_estimator.r")
source("../MainFunctions/bootstrap_correa_estimator.r")
source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
source("../MainFunctions/bootstrap_vasicek_estimator.r")
source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Programs/functions_sample_bias_mse.R")#

set.seed(1234567890, kind = "Mersenne-Twister")

@@

  entropy <- term1 + term2 
  return(entropy)
}

gamma_sar_sample <- function(L, mu, n) {
  samples <- rgamma(n, shape = L, rate = L / mu)
  return(samples)
}

```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR"}
L <- c(1, 3, 8, 12, 100)

L_labels <- c("L = 1", "L = 3", "L = 8", "L = 12", "L = 100")

mu <- seq(0.1, 10, length.out = 500)

entropies <- sapply(L, function(L) entropy_gamma_sar(L, mu))

muEntropy <- data.frame(mu, entropies)

muEntropy.molten <- melt(muEntropy, id.vars = "mu", variable.name = "Looks", value.name = "Entropy")

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = Looks)) +
  geom_line() +
  #theme_minimal() +
  scale_color_manual(values = rainbow(length(L)), labels = L_labels) +
  labs(col = "Looks") +
  xlab(expression(paste(mu)))

@@

```{r 3d_GIO, fig.align="center",  out.width = "120%", fig.cap="Simulation of entropy for ${G}_I^0$. ", fig.show="hold",  fig.pos="hbt"}
knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf")
```
